BIP Architectures and Open pNets

### 2019-01-25 2018-Arch-pNets/arch-pNets.tex
new figures 2 et 3
4.1 et listing/OTs

\begin{figure}[t]
  \centering
  \includegraphics[width=\columnwidth]{TimerOpenAut}
  \caption{The open Automaton of the Failure Monitor Architecture}
  \label{schema:ArchFailure:BIP}
\end{figure}

\begin{figure}[t]
  \centering
  \includegraphics[width=0.8\columnwidth]{FailureTimerOA}
  \caption{The open Automaton of the Failure Monitor Architecture}
  \label{schema:ArchFailure:BIP}
\end{figure}

12 open transitions... Comments on the predicates ???

Should list some temporal logic properties....

@@

INFO  BIPArchFailureTimerMax_LTF3 -
       {t0---init-->t1, s0---init-->s1},   {},  [true],
       {t := 0, z := TopInt, zone := minZone,maxZone}
    OT1 ------------------------------------------------------------
        <t0_s0>-----alpha4----><t1_s1>

INFO  BIPArchFailureTimerMax_LTF3 -
       {t1---tick(z, t, z1)-->t1, s1---fail(zone, false)-->s1},   {---:hb_B-->},
       [(:hb_B=fail(b0:sva_SV0:1:1)/\(t<(GET_MAX z))
         /\((tick(z, t, z1))=(tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))
         /\((fail(zone, false))=(fail(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))
         /\(b1:sva_SV0:1:1=>b0:sva_SV0:1:1)
         /\(z1:sva_SV0:1:1=
         (z:sva_SV0:1:1/\((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt))+t:sva_SV0:1:1)))],
       {t := t+1, z := z1}
    OT2 ------------------------------------------------------------
        <t1_s1>-----alpha0----><t1_s1>

INFO  BIPArchFailureTimerMax_LTF3 -
       {t1---tick(z, t, z1)-->t1, s1---fail(zone, true)-->s2},   {---:hb_B-->},
       [(:hb_B=fail(b0:sva_SV0:1:1)/\(t<(GET_MAX z))
         /\((tick(z,t, z1))=(tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))
         /\((fail(zone, true))=(fail(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))
         /\(b1:sva_SV0:1:1=>b0:sva_SV0:1:1)
         /\(z1:sva_SV0:1:1=
         (z:sva_SV0:1:1/\((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt))+t:sva_SV0:1:1)))],
       {t := t+1, z := z1}
    OT3 ------------------------------------------------------------
        <t1_s1>-----alpha0----><t1_s2>

INFO  BIPArchFailureTimerMax_LTF3 -
       {t1---cancel(false)-->t1, s1---resume(false)-->s1},   {---:hb_B-->},
       [(:hb_B=fail(b0:sva_SV0:1:1)
         /\((cancel(false))=(cancel(b1:sva_SV1:1:2)))
         /\((resume(false))=(resume(b2:sva_SV1:1:2)))
         /\(b1:sva_SV1:1:2=b2:sva_SV1:1:2)],   {}
    OT4 ------------------------------------------------------------
        <t1_s1>-----alpha1----><t1_s1>

INFO  BIPArchFailureTimerMax_LTF3 -
       {t1---timeout-->t1, s1---timeout-->s1},   {---:hb_E-->},
       [(:hb_E=ask)/\(t in z)],   {t := t+1}
    OT5 ------------------------------------------------------------
        <t1_s1>-----alpha2----><t1_s1>

INFO  BIPArchFailureTimerMax_LTF3 -
       {t1---tick(z, t, z1)-->t1, s2---fail(zone, false)-->s2},   {---:hb_B-->},
       [(:hb_B=fail(b0:sva_SV0:1:1)/\(t<(GET_MAX z))
         /\((tick(z, t, z1))=(tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))
         /\((fail(zone, false))=(fail(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))
         /\(b1:sva_SV0:1:1=>b0:sva_SV0:1:1)
         /\(z1:sva_SV0:1:1=
         (z:sva_SV0:1:1/\((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt))+t:sva_SV0:1:1)))],
       {t := t+1, z := z1}
    OT6 ------------------------------------------------------------
        <t1_s2>-----alpha0----><t1_s2>

INFO  BIPArchFailureTimerMax_LTF3 -
       {t1---cancel(false)-->t1, s2---resume(false)-->s2},   {---:hb_B-->},
       [(:hb_B=resume)/\((cancel(false))=(cancel(b1:sva_SV1:1:2)))
         /\((resume(false))=(resume(b2:sva_SV1:1:2)))/\(b1:sva_SV1:1:2=b2:sva_SV1:1:2)],   {}
    OT7 ------------------------------------------------------------
        <t1_s2>-----alpha1----><t1_s2>

INFO  BIPArchFailureTimerMax_LTF3 -
       {t1---cancel(true)-->t1, s2---resume(true)-->s1},   {---:hb_B-->},
       [(:hb_B=resume)/\((cancel(true))=(cancel(b1:sva_SV1:1:2)))
         /\((resume(true))=(resume(b2:sva_SV1:1:2)))/\(b1:sva_SV1:1:2=b2:sva_SV1:1:2)],
       {t := 0, z := TopInt}
    OT8 ------------------------------------------------------------
        <t1_s2>-----alpha1----><t1_s1>

INFO  BIPArchFailureTimerMax_LTF3 -
       {t1---timeout-->t1, s2---timeout-->s3},   {---:hb_E-->},
       [(:hb_E=ask)/\(t in z)],   {t := t+1}
    OT9 ------------------------------------------------------------
        <t1_s2>-----alpha2----><t1_s3>

INFO  BIPArchFailureTimerMax_LTF3 -
       {t1---tick(z, t, z1)-->t1, s3---fail(zone, false)-->s3},   {---:hb_B-->},
       [(:hb_B=fail(b0:sva_SV0:1:1)/\(t<(GET_MAX z))
         /\((tick(z, t, z1))=(tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))
         /\((fail(zone, false))=(fail(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))
         /\(b1:sva_SV0:1:1=>b0:sva_SV0:1:1)
         /\(z1:sva_SV0:1:1=
         (z:sva_SV0:1:1/\((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt))+t:sva_SV0:1:1)))],
       {t := t+1, z := z1}
    OT10 ------------------------------------------------------------
        <t1_s3>-----alpha0----><t1_s3>

INFO  BIPArchFailureTimerMax_LTF3 -
       {t1---cancel(false)-->t1, s3---resume(false)-->s3},   {---:hb_B-->},
       [(:hb_B=resume)/\((cancel(false))=(cancel(b1:sva_SV1:1:2)))
         /\((resume(false))=(resume(b2:sva_SV1:1:2)))/\(b1:sva_SV1:1:2=b2:sva_SV1:1:2)],   {}
    OT11 ------------------------------------------------------------
        <t1_s3>-----alpha1----><t1_s3>

INFO  BIPArchFailureTimerMax_LTF3 -
        {s3---reset-->s1},   {---:hb_E-->},     [(:hb_E=ask)],   {}
    OT12 ------------------------------------------------------
        <t1_s3>-----alpha3----><t1_s1>

INFO  BIPArchFailureTimerMax_LTF3 - Total: 12 SATISFIABLE OTs
INFO  BIPArchFailureTimerMax_LTF3 -        235 UNSATISFIABLE OTs
INFO  BIPArchFailureTimerMax_LTF3 - Total Time: 1293 ms
\end{verbatim}

>>>>

%% \begin{figure}[t]
%%   \centering
%%   \includegraphics[width=\columnwidth]{TimerOpenAut}
%%   \caption{The open Automaton of the Failure Monitor Architecture}
%%   \label{schema:ArchFailure:BIP}
%% \end{figure}

\begin{figure}[t]
  \centering
  \includegraphics[width=0.8\columnwidth]{TimerOADetailed}
  \caption{The open Automaton of the Failure Monitor Architecture}
  \label{schema:ArchFailure:BIP}
\end{figure}

In Figure~\ref{schema:ArchFailure:OA} we show the full open automaton
obtained from our pNet. For reasons of space, we have not shown the
detail of the open transition, but only the assignement of state
variables, and the resulting action. You can find the full details in
Appendix \ref{secn:full-results}. As an example, $OT_3$ is the one explained in Example
\ref{Example:TimerOT3} page \pageref{Example:TimerOT3}

\todoEM{12 open transitions... Comments on the predicates ???}

@@

       {t0---init-->t1, s0---init-->s1},   {},  [true],
       {t := 0, z := TopInt, zone := minZone,maxZone}
    OT1 ------------------------------------------------------------
        <t0_s0>-----init----><t1_s1>

       {t1---tick(z, t, z1)-->t1, s1---fail(zone, false)-->s1},   {---:hb_B-->},
       [(:hb_B=fail(b0:sva_SV0:1:1)/\(t<(GET_MAX z))
         /\((tick(z, t, z1))=(tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))
         /\((fail(zone, false))=(fail(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))
         /\(b1:sva_SV0:1:1=>b0:sva_SV0:1:1)
         /\(z1:sva_SV0:1:1=
         (z:sva_SV0:1:1/\((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt))+t:sva_SV0:1:1)))],
       {t := t+1, z := z1}
    OT2 ------------------------------------------------------------
        <t1_s1>-----fail----><t1_s1>

       {t1---tick(z, t, z1)-->t1, s1---fail(zone, true)-->s2},   {---:hb_B-->},
       [(:hb_B=fail(b0:sva_SV0:1:1)/\(t<(GET_MAX z))
         /\((tick(z,t, z1))=(tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))
         /\((fail(zone, true))=(fail(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))
         /\(b1:sva_SV0:1:1=>b0:sva_SV0:1:1)
         /\(z1:sva_SV0:1:1=
         (z:sva_SV0:1:1/\((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt))+t:sva_SV0:1:1)))],
       {t := t+1, z := z1}
    OT3 ------------------------------------------------------------
        <t1_s1>-----fail----><t1_s2>

       {t1---cancel(false)-->t1, s1---resume(false)-->s1},   {---:hb_B-->},
       [(:hb_B=fail(b0:sva_SV0:1:1)
         /\((cancel(false))=(cancel(b1:sva_SV1:1:2)))
         /\((resume(false))=(resume(b2:sva_SV1:1:2)))
         /\(b1:sva_SV1:1:2=b2:sva_SV1:1:2)],   {}
    OT4 ------------------------------------------------------------
        <t1_s1>-----resume----><t1_s1>

       {t1---timeout-->t1, s1---timeout-->s1},   {---:hb_E-->},
       [(:hb_E=ask)/\(t in z)],   {t := t+1}
    OT5 ------------------------------------------------------------
        <t1_s1>-----ask----><t1_s1>

       {t1---tick(z, t, z1)-->t1, s2---fail(zone, false)-->s2},   {---:hb_B-->},
       [(:hb_B=fail(b0:sva_SV0:1:1)/\(t<(GET_MAX z))
         /\((tick(z, t, z1))=(tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))
         /\((fail(zone, false))=(fail(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))
         /\(b1:sva_SV0:1:1=>b0:sva_SV0:1:1)
         /\(z1:sva_SV0:1:1=
         (z:sva_SV0:1:1/\((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt))+t:sva_SV0:1:1)))],
       {t := t+1, z := z1}
    OT6 ------------------------------------------------------------
        <t1_s2>-----fail----><t1_s2>

       {t1---cancel(false)-->t1, s2---resume(false)-->s2},   {---:hb_B-->},
       [(:hb_B=resume)/\((cancel(false))=(cancel(b1:sva_SV1:1:2)))
         /\((resume(false))=(resume(b2:sva_SV1:1:2)))/\(b1:sva_SV1:1:2=b2:sva_SV1:1:2)],   {}
    OT7 ------------------------------------------------------------
        <t1_s2>-----resume----><t1_s2>

       {t1---cancel(true)-->t1, s2---resume(true)-->s1},   {---:hb_B-->},
       [(:hb_B=resume)/\((cancel(true))=(cancel(b1:sva_SV1:1:2)))
         /\((resume(true))=(resume(b2:sva_SV1:1:2)))/\(b1:sva_SV1:1:2=b2:sva_SV1:1:2)],
       {t := 0, z := TopInt}
    OT8 ------------------------------------------------------------
        <t1_s2>-----resume----><t1_s1>

       {t1---timeout-->t1, s2---timeout-->s3},   {---:hb_E-->},
       [(:hb_E=ask)/\(t in z)],   {t := t+1}
    OT9 ------------------------------------------------------------
        <t1_s2>-----ask----><t1_s3>

       {t1---tick(z, t, z1)-->t1, s3---fail(zone, false)-->s3},   {---:hb_B-->},
       [(:hb_B=fail(b0:sva_SV0:1:1)/\(t<(GET_MAX z))
         /\((tick(z, t, z1))=(tick(z:sva_SV0:1:1, t:sva_SV0:1:1, z1:sva_SV0:1:1)))
         /\((fail(zone, false))=(fail(zone:sva_SV0:1:1, b1:sva_SV0:1:1)))
         /\(b1:sva_SV0:1:1=>b0:sva_SV0:1:1)
         /\(z1:sva_SV0:1:1=
         (z:sva_SV0:1:1/\((b1:sva_SV0:1:1?(zone:sva_SV0:1:1)TopInt))+t:sva_SV0:1:1)))],
       {t := t+1, z := z1}
    OT10 ------------------------------------------------------------
        <t1_s3>-----fail----><t1_s3>

       {t1---cancel(false)-->t1, s3---resume(false)-->s3},   {---:hb_B-->},
       [(:hb_B=resume)/\((cancel(false))=(cancel(b1:sva_SV1:1:2)))
         /\((resume(false))=(resume(b2:sva_SV1:1:2)))/\(b1:sva_SV1:1:2=b2:sva_SV1:1:2)],   {}
    OT11 ------------------------------------------------------------
        <t1_s3>-----resume----><t1_s3>

        {s3---reset-->s1},   {---:hb_E-->},     [(:hb_E=ask)],   {}
    OT12 ------------------------------------------------------
        <t1_s3>-----reset----><t1_s1>

INFO  BIPArchFailureTimerMax - Total: 12 SATISFIABLE OTs
INFO  BIPArchFailureTimerMax -        235 UNSATISFIABLE OTs
INFO  BIPArchFailureTimerMax - Total Time: 1293 ms
\end{verbatim}
